---
title: My Neighbor Totoro 
author: Aaron
output:
  BiocStyle::html_document:
    toc_float: yes
vignette: >
  %\VignetteIndexEntry{My Neighbor Totoro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---   

```{r, cache=FALSE, echo=FALSE}
knitr::opts_chunk$set(error=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
```

```{r, cache=FALSE, echo=FALSE, results="hide"}
BiocWorkCache:::.compiler("test1")
```

# Introduction

When talking about Ghibli, you can't go past **My Neighbor Totoro**.

```{r}
readLines("chipseq.log")
```

# Method

It's classic slice-of-life with a bit of magic thrown in.

```{r}
Y <- runif(1000)
mean(Y)
```

# Results

The Cat Bus is particularly memorable. 
Looks pretty comfortable if you don't have motion sickness and aren't allergic to cats.

```{r}
se <- readRDS("castle_in_the_sky.rds")
se$blob <- runif(ncol(se))
se
```

# Discussion

The moral of the story is - offer your umbrella to others, even if they're a bit weird.

```{r}
saveRDS(se, file="my_neighbor_totoro.rds")
```

# Session information

```{r}
sessionInfo()
```
