---
title: Castle in the Sky 
author: Aaron
output:
  BiocStyle::html_document:
    toc_float: yes
vignette: >
  %\VignetteIndexEntry{Castle in the Sky}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---   

```{r, echo=FALSE, cache=FALSE}
knitr::opts_chunk$set(error=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
```

# Introduction

One of my favorite movies of all time is **Castle in the Sky**.

```{r}
write(file="~/chipseq.log", as.character(Sys.time()), append=TRUE)
readLines("~/chipseq.log")
```

# Method

I'm a big sucker for airships and floating stuff, and the soundtrack is stellar.

```{r, cached=TRUE}
X <- rnorm(1000)
summary(X)
```

# Results

Did you know that the bad guy was voiced by Mark Hamill in the English dub?

```{r}
library(SummarizedExperiment)
se <- SummarizedExperiment(list(counts=matrix(runif(1000), ncol=10)))
se$blah <- sample(LETTERS, ncol(se))
se
```

# Discussion

I actually have a **Castle in the Sky** T-shirt, though it's subtle enough that most people don't get the reference.

```{r}
saveRDS(se, file="castle_in_the_sky.rds")
```

# Session information

```{r}
sessionInfo()
```
